\documentclass[12pt,letterpaper]{ntdhw}


\title{Project 0: Symbolic Reasoning}
\author{CSCI 534 -- Robot Planning and Manipulation}

\rhead{Names: PUT-YOUR-NAMES-HERE}

%\keytrue

\begin{document}
\pagestyle{fancyplain}

\maketitle
\thispagestyle{fancyplain}
%\clearpage

\begin{enumerate}

  \item (10pt) Part of the purpose of this initial project is to give
  you time to set up and learn to use an interactive Lisp development
  environment such as SLIME.  Using such an environment will help you
  complete the next project.  Please provide a screenshot of the Lisp
  environment on your system.  (Just calling Lisp from the shell will
  make development more difficult and is not an acceptable answer for
  this question.)

  \item (10pt) Describe, in general terms, how a recursive function operates.
  How can we ensure that a recursive function terminates?

  \item (10pt) Why is garbage collection important for the symbolic
  algorithms implemented in this project?

  \item We represent S-expressions in memory with single-linked lists.
  \begin{enumerate}
    \item (5pt) Why don't we use doubly-linked lists for S-expression?
    \item (5pt) Why don't we use arrays for S-expressions?
  \end{enumerate}

  \item Similarly to the symbolic differentiation in this project, we
  could also implement symbolic integration.  In practice, numerical
  integration is commonly used.
  \begin{enumerate}
    \item (5pt) When would it be preferable/necessary to use symbolic integration?
    \item (5pt) When would it be preferable/necessary to use numerical integration?
  \end{enumerate}



\end{enumerate}

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
